### 2012-08-17 novela.tex

\documentclass[11pt,twoside,openright,a5paper]{book}

\usepackage[a5paper]{geometry}

\usepackage{times}
\usepackage[Lenny]{fncychap}
%\usepackage[Conny]{fncychap}

\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\newcommand{\personaje}{Nombre del personaje}

\title{Título}
\author{Autor}
\date{}

\hyphenation{o-pe-ra-cio-nes}

\begin{document}

\pagestyle{plain}

\maketitle

\tableofcontents

\chapter*{Prólogo}
\addcontentsline{toc}{chapter}{Prólogo}

texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto
texto texto texto texto texto texto texto texto 
texto texto texto texto texto texto texto texto
texto texto texto

\chapter{Título Capítulo}
\input{cap1.tex}

\end{document}