### 2014-01-26 cuentos5/historiasDeDosQueNoSonUno.tex

\chapter*{El primer romántico} \addcontentsline{toc}{chapter}{El primer romántico}

\input{primerRomantico.txt}

\chapter*{El departamento} \addcontentsline{toc}{chapter}{El departamento}

\input{elDepartamento.txt}

\chapter*{Libros marcados} \addcontentsline{toc}{chapter}{Libros marcados}

\input{librosMarcados.txt}

\chapter*{Dos palabras} \addcontentsline{toc}{chapter}{Dos palabras}

\input{dosPalabras.txt}

\chapter*{Encuentro dominical} \addcontentsline{toc}{chapter}{Encuentro dominical}

\input{encuentroDominical.txt}

\chapter*{Mameluco} \addcontentsline{toc}{chapter}{Mameluco}

\input{mameluco.txt}

\chapter*{Se despertó} \addcontentsline{toc}{chapter}{Se despertó}

\input{seDesperto.txt}

\chapter*{Naranjas para don Bordesio} \addcontentsline{toc}{chapter}{Naranjas para don Bordesio}

\input{naranjas.txt}